The pollination trade-off

### 2018-08-17 paper/supp-info.Rmd
Fix figure of relative abundance
Close #13

```{r fig-abundance-logtransformed-or-not, fig.height = 2, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been "}
drake::loadd(fig_abundance)

cowplot::plot_grid(
  fig_abundance[[2]], 
  fig_abundance[[2]],
  rel_widths = c(0.42, 0.58), labels = LETTERS[1:2], label_size = 8)
```

```{r table-species-gain-global, results = 'asis'}
drake::loadd(significant_gain_global, significant_gain_site, sites)
glance_table(significant_gain_global) %>%
  dplyr::select(recipient, estimate, statistic, p.value) %>%
  dplyr::mutate(recipient = paste0('{\\emph{ ', recipient, '}}')) %>%
  dplyr::rename(`p value` = p.value,
         `difference` = estimate,
         `plant species` = recipient) %>%
  knitr::kable(
    caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers. Tests were performed at the species level (across communities).", 
    escape = FALSE, 
    booktabs = TRUE, 
    linesep = c("")) %>%
  kableExtra::kable_styling(font_size = 8)
```

@@

cowplot::plot_grid(plotlist = site_plots_conspecific, ncol = 3)

```

>>>>

```{r fig-abundance-logtransformed-or-not, fig.height = 2, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been log transformed and scaled to have a mean of zero and a standard deviation of one."}
drake::loadd(fig_abundance)

cowplot::plot_grid(
  fig_abundance[[2]], 
  fig_abundance[[1]],
  rel_widths = c(0.42, 0.58), labels = LETTERS[1:2], label_size = 8)
```

```{r table-species-gain-global, results = 'asis'}
drake::loadd(significant_gain_global, significant_gain_site, sites)

glance_table(significant_gain_global) %>%
  dplyr::select(recipient, estimate, statistic, p.value) %>%
  dplyr::mutate(recipient = paste0('{\\emph{ ', recipient, '}}')) %>%
  dplyr::rename(`p value` = p.value,
         `difference` = estimate,
         `plant species` = recipient) %>%
  knitr::kable(
    caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers. Tests were performed at the species level (across communities).", 
    escape = FALSE, 
    booktabs = TRUE, 
    linesep = c("")) %>%
  kableExtra::kable_styling(font_size = 8)
```

@@

cowplot::plot_grid(plotlist = site_plots_conspecific, ncol = 3)
```
